---
title: "Using the Template Package"
bibliography: [references.bib]
biblio-style: apalike
link-citations: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

remotes::install_cran(c("desc"), repos = "https://cran.rstudio.com/", quiet = TRUE)
desc_obj <- desc::description$new()
package_name <- desc_obj$get_field("Package")
```

```{r setup}
```

This article describes how to use the template for a new package. The *Overview*
section presents a recipe that leads to a fully configure package. The rest of
the sections illustrate some of the steps. For more general information about R
package development, refer to [@wickham2015r].

## Overview

The following steps set up:

* Essential configurations for deploying an R package locally and on GitHub; and
* Information about the package and the development team.

To use the template for a new package, follow the next steps:

1. Choose a package name:
  * Do use the following characters: letters (uppercase or uppercase), digits
  and dot ("."); and
  * Don’t use spaces, underscores or hyphens. Instead, use camelCase or dots to
  separate words.
2. Create a new repo on GitHub; name the repo after the package name; 
3. Copy the content of **template.package** into the new repo;
4. Delete the `vignettes` folder;
5. Rename `template.package.Rproj` to `{package-name}.Rproj`;
6. Update the following fields within the DESCRIPTION file:
  * **Package**; rename the package name.
  *	**Title**; describe the package in one line:
    * It should be plain text (no markup), capitalised like a title, and NOT end
    in a period; and
    * Keep it short: listings truncate the title to 65 characters.
  * **URL**; Add a link pointing at the GitHub pages address of the package:
    * Use the template: https://{user-name}.github.io/{package-name}/
    * For example https://tidylab.github.io/template.package/
  * **BugReports**; edit the URL such that it leads to the package issue page:
    * Use the template: https://github.com/{user-name}/{package-name}/issues
    * For example https://github.com/tidylab/template.package/issues
  * **Date**; replace with the creation date of the package:
    * The specified date determines the MRAN snapshot date; alternatively 
    * Use the most recent packages on CRAN by removing that filed.
  * **Authors** and **Maintainer**: Update persons information;
  * **Description**; Elaborate the package **Title**:
    * You can use multiple sentences but you are limited to one paragrap; and
    * If your description spans multiple lines (and it should!), each line must
    be no more than 80 characters wide. Indent subsequent lines with 4 spaces
7. Render the `README.Rmd` file. By default, README.Rmd displays package
information gathered from the DESCRIPTION file;
8. Push changes to GitHub;
9. Connect the GitHub repo to external services:
  * Go to GitHub user *Settings/Developer settings/Personal access tokens* and
  generate a token named *GITHUB_PAT*; then
  *	Go to [Travis website](https://travis-ci.org/), add the project and enable
  its integration. Add *GITHUB_PAT* as an environment variable; then
  * Go to [Codecov website](https://codecov.io/gh), add the project and enable
  its integration.

<!-- ## Step by Step -->

## References
